Constructing a universe for the setoid model

### 2020-10-14 paper.tex
small fixes

As an example, consider the following definition of a small universe with
bool and $\Pi$.
\vspace{-0.2em}
\begin{minipage}{0.45\textwidth}
\begin{align*}
  & \textsf{data}\ \U\ : \mType \\
  & \quad \textsf{bool} : \U \\
  & \quad \textsf{pi} : (A : \U) \to (\El\ A \to \U) \to \U \\
\end{align*}
\end{minipage}
\begin{minipage}{0.45\textwidth}
\begin{align*}
  & \El\ : \U \to \mType \\
  & \El\ \textsf{bool} :\equiv \mathbbm{2} \\
  & \El\ (\textsf{pi}\ A\ B) :\equiv (a : \El\ A) \to \El\ (B\ a) \\
\end{align*}
\end{minipage}

@@

We will follow the method outlined in Section~\ref{ir-universes}. In
addition to $\inU$ for defining $\U$, we also introduce a family
$\inUU$ of binary relations between types in the universe, from which we
then define $\_\sim_{\setoidU}\_$.
\vspace{-0.2em}
\begin{align*}
  & \textsf{data}\ \inU : \mType \to \mType_1 \\
  & \qquad \textsf{bool} : \inU\ \mathbbm{2} \\
  & \qquad \pi : \forall\{A\;A_\sim\;B\;B_\sim\}(a : \inU\;A)
  (b : (x : A) \to \inU\;(B\;x))\\
  & \qquad\ \to \inU\;a\;a\;A_\sim \to (\forall\{x_0\;x_1\}(x_{01} : A_\sim\;x_0\;x_1)
  \to \inUU\;(b\;x_0)\;(b\;x_1)\;(B_\sim\;x_{01})) \\
  & \qquad\ \to \inU\;
  (\Sigma\;(f : (x : A) \to B\;x) \\
  &\qquad\qquad\qquad\quad\, ((x_0\;x_1 : A)(x_{01} : A_\sim\;x_0\;x_1) \to B_\sim\;x_{01}\;(f\;x_0)\;(f\;x_1))) \\
  %%%%%%
  & \textsf{data}\ \inUU : \{A\ A' : \mType\} \to \inU\ A \to \inU\ A' \to (A \to A' \to \mProp) \to \mType_1 \\
  & \qquad \mathsf{bool}_\sim : \inUU\;\textsf{bool}\;\textsf{bool}\;
  (\lambda x_0\;x_1\; .\; x_0 \stackrel{?}{=}_{\mathbbm{2}} x_1) \\
  & \qquad \pi_\sim :
  \forall\{A_0\;A_1\;A_{0\sim}\;A_{01\sim}\;B_0\;B_1\;B_{0\sim}\;B_{1\sim}\;B_{01\sim}\}
  \{ a_0 : \inU\;A_0 \}\{ a_1 : \inU\;A_1 \}\\
  & \qquad\quad\quad\ \; \{b_0 : (x_0 : A_0) \to \inU\;(B_0\;x_0)\}
  \{b_1 : (x_1 : A_1) \to \inU\;(B_1\;x_1)\}\\
  & \qquad\quad\quad\ \; \{a_{0\sim} : \inUU\;a_0\;a_0\;A_{0\sim}\}
  \{a_{1\sim} : \inUU\;a_1\;a_1\;A_{1\sim}\} \\
  & \qquad\quad\quad\ \; \{ b_{0\sim} : \forall\{x_0\;x_1\}(x_{01} : A_{0\sim}\;x_0\;x_1)
    \to \inUU\;(b_0\;x_0)\;(b_0\;x_1)\;(B_{0\sim}\;x_{01}) \}\\
  & \qquad\quad\quad\ \; \{ b_{1\sim} : \forall\{x_0\;x_1\}(x_{01} : A_{1\sim}\;x_0\;x_1)
    \to \inUU\;(b_1\;x_0)\;(b_1\;x_1)\;(B_{1\sim}\;x_{01}) \}\\
  & \qquad\quad \to \inUU\;a_0\;a_1\;A_{01\sim} \\
    & \qquad\quad \to (\forall\{x_0\;x_1\}(x_{01} : A_{01\sim}\;x_0\;x_1)
      \to \inUU\;(b_0\;x_0)\;(b_1\;x_1)\;(B_{01\sim}\;x_{01})) \\
  & \qquad\quad \to \inUU\;(\pi\;a_0\;a_{0\sim}\;b_0\;b_{0\sim})\;
      (\pi\;a_1\;a_{1\sim}\;b_1\;b_{1\sim}) \\
  & \qquad\qquad\qquad\quad\,(\lambda f_0\;f_1\;.\;\forall(x_0\;x_1)\to A_{01\sim}\;x_0\;x_1
        \to B_{01\sim}\;x_{01}\;(\pi_1\;f_0\;x_0)\;(\pi_1\;f_1\;x_1))
\end{align*}

Just as the role of $\inU$ is, as before, to classify all types that are image
of $\El$, in the same way $\inUU\ p\ q$ classifies all relations of type $A \to
A' \to \mProp$ that are image of $\_\vdash\_\sim_{\El}\_$, given proofs $p :
\inU\ A, q : \inU\ A'$.
%
In particular, this definition of $\inUU$ states that the appropriate
equivalence for boolean elements is the obvious syntactic equality
$\_\stackrel{?}{=}_{\mathbbm{2}}\_$, whereas functions are to be compared
pointwise.
%
Note that $\inU$ appears in the sort of $\inUU$. Since these types are
mutually defined, they form an instance of \emph{induction-induction}, a schema
that allows the definition of a type mutually with other types that contain the
first one in their signature \cite{ii}.\footnote{The main example of
  induction-induction is the intrinsic definition of a dependent type theory in
  type theory \cite{tt-in-tt}.}

@@

What is left now is to define the setoid equality relation on the universe, as
well as the setoid equality relation on $\El\ A$ for any $A$ in $\setoidU$.
%
Two codes $A, B$ in the universe $\setoidU$ are equal when there exists a setoid
equivalence relation on their respective sets $\El\ A$ and $\El\ B$. Intuitively,
since elements of a setoid are only ever compared to elements of the same
setoid, this should only be possible if $A$ and $B$ are codes for the same setoid,
that is, if $A \sim_{\setoidU} B$. Existence and well-formedness of such
relations is expressed via the type $\inUU$ just defined, hence we would
expect $A \sim_{\setoidU} B$ to be defined as follows:
\[
(A, p_A) \sim_{\setoidU} (B, p_B) :\equiv \Sigma\ (R: A \to B \to \mProp)\ (\inUU\ p_A\ p_B\ R)
\]

Unfortunately this definition only manages to capture the idea, but does not
actually typecheck. In fact, $\_\sim_{\setoidU}\_$ should be $\mProp_1$-valued
relation, so $A \sim_{\setoidU} B$ should be a proposition. However, the
$\Sigma$ type shown above clearly isn't, since it quantifies over a type of
relations, which is not a proposition.
%
One possible solution is actually quite simple, and it just involves truncating
the $\Sigma$ type above to force it to be in $\mProp_1$.
\vspace{-0.2em}
\begin{align*}
  & \_\sim_{\setoidU}\_ : \setoidU \to \setoidU \to \mProp_1 \\
  & (X , p) \sim_{\setoidU} (X' , p') =
   \ \parallel \Sigma\ (R : X \to X' \to \mProp)\ (\inUU\ p\ p'\ R) \parallel
\end{align*}

We are now left to define the indexed equivalence relation on $\El$:
\vspace{-0.2em}
\begin{align*}
  & \_\vdash\_\sim_{\El}\_ : \{A\ B : \U\} \to A\ \sim_{\setoidU}\ B \to \El\ A \to \El\ B \to \mProp \\
  & p \vdash a \sim_{\El} b :\equiv \ ?
\end{align*}

In the definition above, $p$ has type $\parallel \Sigma\ (R: \El\,A \to \El\,B \to
\mProp)\ (...) \parallel$. If the type wasn't propositionally truncated, we could define
$p \vdash a \sim_{\El} b$ by extracting the relation out of the first component
of $p$, and apply it to $a, b$. That is, $p \vdash a \sim_{\El} b :\equiv
\pi_1\,p\,a\,b$. This would make the definition of $\_\sim_\setoidU\_$ and
$\_\vdash\_\sim_{\El}\_$ in line with how we defined $\setoidU$ and $\El$.

However, this doesn't work in our case, since the type of $p$ \emph{is}
propositionally truncated, hence it cannot be eliminated to construct a
proof-relevant object.
%
Fortunately, we can work around this limitation by defining $p \vdash x
\sim_{\El} y$ by induction on the codes $A\ B : \setoidU$, in a way that ends
up being logically equivalent to the proposition we would have obtained by
$\mathsf{proj}_1\ p\ x\ y$ if there were no truncation.
%
More precisely, we need to construct proofs that for any concrete $R$ and
$\mathsf{inR}$, the types $| (R, \mathsf{inR}) | \vdash x \sim_{\El} y$ and $R\ x\ y$
are logically equivalent. These in turn need to be defined mutually with
$\_\vdash\_\sim_{\El}\_$. We direct the interested reader to the Agda
formalization for the full details of these definitions, as they are quite
involved.

@@

Contexts in \textsf{Con} are formed out of empty contexts $\bullet$ and context
extension $\_,\_$. Types in \textsf{Ty} are either the base type $\iota$ or
$\Pi$ types.
\vspace{-0.2em}
\begin{alignat*}{10}
  & \bullet && : \textsf{Con}                                                          &&  \iota && : (\GG : \textsf{Con}) \to \textsf{Ty}\ \GG \\
  & \_,\_ && : (\GG : \textsf{Con}) \to \textsf{Ty}\ \GG \to \textsf{Con} \hspace{5em} &&  \Pi && : \{\GG : \textsf{Con}\} (A : \textsf{Ty}\ \GG) \to \textsf{Ty}\ (\GG , A) \to \textsf{Ty}\ \GG
\end{alignat*}

@@

The definition of the codes and predicate types follows that of the original
inductive-inductive type, and can be derived systematically from it. More
importantly, they can be defined without induction-induction, since although
$\textsf{Con}_0$ and $\textsf{Ty}_0$ are defined mutually, their sorts are not
indexed. \\
\vspace{-0.2em}
\begin{minipage}{0.4\textwidth}
\begin{alignat*}{10}
  & \bullet_0 && : \textsf{Con}_0 \\
  & \_,_0\_ && : (\GG : \textsf{Con}_0) \to \textsf{Ty}_0 \to \textsf{Con}_0 \\
  & \iota_0 && : (\GG : \textsf{Con}_0) \to \textsf{Ty}_0 \\
  & \Pi_0 && : \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \hspace{2.8em} \\
\end{alignat*}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\vspace{-1.3em}
\begin{alignat*}{10}
  & \bullet_1 && : \textsf{Con}_1\ \bullet_0 \\
  & \_,_1\_ && : \forall\{\GG_0\ A_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ A_0 \\
  & && \to \textsf{Con}_1\ (\GG_0 \,,_0 A_0) \\
  & \iota_1 && : \forall\{\GG_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ (\iota_0\ \GG_0) \\
  & \Pi_1 && : \forall\{\GG_0\ A_0\ B_0\} \to \textsf{Con}_1\ \GG_0 \\
  & && \to \textsf{Ty}_1\ \GG_0\ A_0 \to \textsf{Ty}_1\ (\GG_0\, ,_0 A_0)\ B_0 \\
  & && \to \textsf{Ty}_1\ \GG_0\ (\Pi_0\ \GG_0\ A_0\ B_0)
\end{alignat*}
\end{minipage}
\\

@@

Let us go back to our \textsf{Con}/\textsf{Ty} example. Given any dependent
algebra of $\textsf{Con}$ and $\textsf{Ty}$ with motives $C : \textsf{Con} \to
\mType$ and $T : (\GG : \textsf{Con}) \to \textsf{Ty}\ \GG \to C\ \GG \to
\mType$, the general eliminators have the following signatures:
\begin{align*}
  & \textsf{elim}_{\textsf{Con}} : (\GG : \textsf{Con}) \to C\ \GG \hspace{5em} \\
  & \textsf{elim}_{\textsf{Ty}} : \{\GG : \textsf{Con}\} (A : \textsf{Ty}\ \GG) \to T\ \GG\ A\ (\textsf{elim}_{\textsf{Con}}\ \GG)
\end{align*}

These can be derived from our encoding of $\textsf{Con}$ and $\textsf{Ty}$ via
untyped codes and well-typing predicates. The way to do it is to first define
the graph of the eliminators in the form of inductively-generated relations:
\begin{align*}
  & \textsf{data}\ \textsf{R-Con} :
    (\GG : \textsf{Con}) \to C\ \GG \to \mType \\
  & \textsf{data}\ \textsf{R-Ty} : \{\GG : \textsf{Con}\} (A : \textsf{Ty}\ \GG)
  (\gamma : C\ \GG)
  \to T\ \GG\ A\ \gamma
  \to \mType
\end{align*}

>>>>

As an example, consider the following definition of a small universe with
bool and $\Pi$. \\
\vspace{-0.2em}
\begin{minipage}{0.45\textwidth}
\begin{align*}
  & \textsf{data}\ \U\ : \mType \\
  & \quad \textsf{bool} : \U \\
  & \quad \textsf{pi} : (A : \U) \to (\El\ A \to \U) \to \U \\
\end{align*}
\end{minipage}
\begin{minipage}{0.45\textwidth}
\begin{align*}
  & \El\ : \U \to \mType \\
  & \El\ \textsf{bool} :\equiv \mathbbm{2} \\
  & \El\ (\textsf{pi}\ A\ B) :\equiv (a : \El\ A) \to \El\ (B\ a) \\
\end{align*}
\end{minipage}

@@

We will follow the method outlined in Section~\ref{ir-universes}. In
addition to $\inU$ for defining $\U$, we also introduce a family
$\inUU$ of binary relations between types in the universe, from which we
then define $\_\sim_{\setoidU}\_$.
\vspace{-0.2em}
\begin{align*}
  & \textsf{data}\ \inU : \mType \to \mType_1 \\
  & \qquad \textsf{bool} : \inU\ \mathbbm{2} \\
  & \qquad \pi : \forall\{A\;A_\sim\;B\;B_\sim\}(a : \inU\;A)
  (b : (x : A) \to \inU\;(B\;x))\\
  & \qquad\ \to \inUU\;a\;a\;A_\sim \to (\forall\{x_0\;x_1\}(x_{01} : A_\sim\;x_0\;x_1)
  \to \inUU\;(b\;x_0)\;(b\;x_1)\;(B_\sim\;x_{01})) \\
  & \qquad\ \to \inU\;
  (\Sigma\;(f : (x : A) \to B\;x) \\
  &\qquad\qquad\qquad\quad\, ((x_0\;x_1 : A)(x_{01} : A_\sim\;x_0\;x_1) \to B_\sim\;x_{01}\;(f\;x_0)\;(f\;x_1))) \\
  %%%%%%
  & \textsf{data}\ \inUU : \{A\ A' : \mType\} \to \inU\ A \to \inU\ A' \to (A \to A' \to \mProp) \to \mType_1 \\
  & \qquad \mathsf{bool}_\sim : \inUU\;\textsf{bool}\;\textsf{bool}\;
  (\lambda x_0\;x_1\; .\; x_0 \stackrel{?}{=}_{\mathbbm{2}} x_1) \\
  & \qquad \pi_\sim :
  \forall\{A_0\;A_1\;A_{0\sim}\;A_{1\sim}\;A_{01\sim}\;B_0\;B_1\;B_{0\sim}\;B_{1\sim}\;B_{01\sim}\}
  \{ a_0 : \inU\;A_0 \}\{ a_1 : \inU\;A_1 \}\\
  & \qquad\quad\quad\ \; \{b_0 : (x_0 : A_0) \to \inU\;(B_0\;x_0)\}
  \{b_1 : (x_1 : A_1) \to \inU\;(B_1\;x_1)\}\\
  & \qquad\quad\quad\ \; \{a_{0\sim} : \inUU\;a_0\;a_0\;A_{0\sim}\}
  \{a_{1\sim} : \inUU\;a_1\;a_1\;A_{1\sim}\} \\
  & \qquad\quad\quad\ \; \{ b_{0\sim} : \forall\{x_0\;x_1\}(x_{01} : A_{0\sim}\;x_0\;x_1)
    \to \inUU\;(b_0\;x_0)\;(b_0\;x_1)\;(B_{0\sim}\;x_{01}) \}\\
  & \qquad\quad\quad\ \; \{ b_{1\sim} : \forall\{x_0\;x_1\}(x_{01} : A_{1\sim}\;x_0\;x_1)
    \to \inUU\;(b_1\;x_0)\;(b_1\;x_1)\;(B_{1\sim}\;x_{01}) \}\\
  & \qquad\quad \to \inUU\;a_0\;a_1\;A_{01\sim} \\
    & \qquad\quad \to (\forall\{x_0\;x_1\}(x_{01} : A_{01\sim}\;x_0\;x_1)
      \to \inUU\;(b_0\;x_0)\;(b_1\;x_1)\;(B_{01\sim}\;x_{01})) \\
  & \qquad\quad \to \inUU\;(\pi\;a_0\;a_{0\sim}\;b_0\;b_{0\sim})\;
      (\pi\;a_1\;a_{1\sim}\;b_1\;b_{1\sim}) \\
  & \qquad\qquad\qquad\quad\,(\lambda f_0\;f_1\;.\;\forall(x_0\;x_1)\to A_{01\sim}\;x_0\;x_1
        \to B_{01\sim}\;x_{01}\;(\pi_1\;f_0\;x_0)\;(\pi_1\;f_1\;x_1))
\end{align*}

Just as the role of $\inU$ is, as before, to classify all types that are image
of $\El$, in the same way $\inUU\ a\ a'$ classifies all relations of type $A \to
A' \to \mProp$ that are image of $\_\vdash\_\sim_{\El}\_$, given proofs $a :
\inU\ A, a' : \inU\ A'$.
%
In particular, this definition of $\inUU$ states that the appropriate
equivalence for boolean elements is the obvious syntactic equality
$\_\stackrel{?}{=}_{\mathbbm{2}}\_$, whereas functions are to be compared
pointwise.
%
Note that $\inU$ appears in the sort of $\inUU$. Since these types are
mutually defined, they form an instance of \emph{induction-induction}, a schema
that allows the definition of a type mutually with other types that contain the
first one in their signature \cite{ii}.\footnote{The main example of
  induction-induction is the intrinsic definition of a dependent type theory in
  type theory \cite{tt-in-tt}.}

@@

What is left now is to define the setoid equality relation on the universe, as
well as the setoid equality relation on $\El\ A$ for any $A$ in $\setoidU$.
%
Two codes $A, B$ in the universe $\setoidU$ are equal when there exists a setoid
equivalence relation on their respective sets $\El\ A$ and $\El\ B$. Intuitively,
since elements of a setoid are only ever compared to elements of the same
setoid, this should only be possible if $A$ and $B$ are codes for the same setoid,
that is, if $A \sim_{\setoidU} B$. Existence and well-formedness of such
relations is expressed via the type $\inUU$ just defined, hence we would
expect $A \sim_{\setoidU} B$ to be defined as follows:
\[
(A, a) \sim_{\setoidU} (B, b) :\equiv \Sigma\ (R: A \to B \to \mProp)\ (\inUU\ a\ b\ R)
\]

Unfortunately this definition only manages to capture the idea, but does not
actually typecheck. In fact, $\_\sim_{\setoidU}\_$ should be $\mProp_1$-valued
relation, so $A \sim_{\setoidU} B$ should be a proposition. However, the
$\Sigma$ type shown above clearly isn't, since it quantifies over a type of
relations, which is not a proposition.
%
One possible solution is actually quite simple, and it just involves truncating
the $\Sigma$ type above to force it to be in $\mProp_1$.
\vspace{-0.2em}
\begin{align*}
  & \_\sim_{\setoidU}\_ : \setoidU \to \setoidU \to \mProp_1 \\
  & (A , a) \sim_{\setoidU} (B , b) =
   \ \parallel \Sigma\ (R : A \to B \to \mProp)\ (\inUU\ a\ b\ R) \parallel
\end{align*}

We are now left to define the indexed equivalence relation on $\El$:
\vspace{-0.2em}
\begin{align*}
  & \_\vdash\_\sim_{\El}\_ : \{A\ B : \U\} \to A\ \sim_{\setoidU}\ B \to \El\ A \to \El\ B \to \mProp \\
  & p \vdash x \sim_{\El} y :\equiv \ ?
\end{align*}

In the definition above, $p$ has type $\parallel \Sigma\ (R: \El\,A \to \El\,B \to
\mProp)\ (...) \parallel$. If the type wasn't propositionally truncated, we could define
$p \vdash x \sim_{\El} y$ by extracting the relation out of the first component
of $p$, and apply it to $x, y$. That is, $p \vdash x \sim_{\El} y :\equiv
\pi_1\,p\,x\,y$. This would make the definition of $\_\sim_\setoidU\_$ and
$\_\vdash\_\sim_{\El}\_$ in line with how we defined $\setoidU$ and $\El$.

However, this doesn't work in our case, since the type of $p$ \emph{is}
propositionally truncated, hence it cannot be eliminated to construct a
proof-relevant object.
%
Fortunately, we can work around this limitation by defining $p \vdash x
\sim_{\El} y$ by induction on the codes $A\ B : \setoidU$, in a way that ends
up being logically equivalent to the proposition we would have obtained by
$\pi_1\ p\ x\ y$ if there were no truncation.
%
More precisely, we need to construct proofs that for any concrete $R$ and
$\mathsf{inR}$, the types $| (R, \mathsf{inR}) | \vdash x \sim_{\El} y$ and $R\ x\ y$
are logically equivalent. These in turn need to be defined mutually with
$\_\vdash\_\sim_{\El}\_$. We direct the interested reader to the Agda
formalization for the full details of these definitions, as they are quite
involved.

@@

Contexts in \textsf{Con} are formed out of empty contexts $\bullet$ and context
extension $\_,\_$. Types in \textsf{Ty} are either the base type $\iota$ or
$\Pi$ types.
\vspace{-0.2em}
\begin{alignat*}{10}
  & \bullet && : \textsf{Con}                                                          &&  \iota && : (\GG : \textsf{Con}) \to \textsf{Ty}\ \GG \\
  & \_,\_ && : (\GG : \textsf{Con}) \to \textsf{Ty}\ \GG \to \textsf{Con} \hspace{3em} &&  \Pi && : \{\GG : \textsf{Con}\} (A : \textsf{Ty}\ \GG) \to \textsf{Ty}\ (\GG , A) \to \textsf{Ty}\ \GG
\end{alignat*}

@@

The definition of the codes and predicate types follows that of the original
inductive-inductive type, and can be derived systematically from it. More
importantly, they can be defined without induction-induction, since although
$\textsf{Con}_0$ and $\textsf{Ty}_0$ are defined mutually, their sorts are not
indexed. \\
\vspace{-0.2em}
\begin{minipage}{0.4\textwidth}
\begin{alignat*}{10}
  & \bullet_0 && : \textsf{Con}_0 \\
  & \_,_0\_ && : \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Con}_0 \\
  & \iota_0 && : \textsf{Con}_0 \to \textsf{Ty}_0 \\
  & \Pi_0 && : \textsf{Con}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \to \textsf{Ty}_0 \hspace{2.8em} \\
\end{alignat*}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\vspace{-1.3em}
\begin{alignat*}{10}
  & \bullet_1 && : \textsf{Con}_1\ \bullet_0 \\
  & \_,_1\_ && : \forall\{\GG_0\ A_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ A_0 \\
  & && \to \textsf{Con}_1\ (\GG_0 \,,_0 A_0) \\
  & \iota_1 && : \forall\{\GG_0\} \to \textsf{Con}_1\ \GG_0 \to \textsf{Ty}_1\ \GG_0\ (\iota_0\ \GG_0) \\
  & \Pi_1 && : \forall\{\GG_0\ A_0\ B_0\} \to \textsf{Con}_1\ \GG_0 \\
  & && \to \textsf{Ty}_1\ \GG_0\ A_0 \to \textsf{Ty}_1\ (\GG_0\, ,_0 A_0)\ B_0 \\
  & && \to \textsf{Ty}_1\ \GG_0\ (\Pi_0\ \GG_0\ A_0\ B_0)
\end{alignat*}
\end{minipage}
\\

@@

Let us go back to our \textsf{Con}/\textsf{Ty} example. Given any dependent
algebra of $\textsf{Con}$ and $\textsf{Ty}$ with motives $C : \textsf{Con} \to
\mType$ and $T : (\GG : \textsf{Con}) \to \textsf{Ty}\ \GG \to C\ \GG \to
\mType$, the general eliminators have the following signatures:
\begin{alignat*}{10}
  & \textsf{elim}_{\textsf{Con}} && : (\GG : \textsf{Con}) \to C\ \GG \hspace{5em} \\
  & \textsf{elim}_{\textsf{Ty}} && : \{\GG : \textsf{Con}\} (A : \textsf{Ty}\ \GG) \to T\ \GG\ A\ (\textsf{elim}_{\textsf{Con}}\ \GG)
\end{alignat*}

These can be derived from our encoding of $\textsf{Con}$ and $\textsf{Ty}$ via
untyped codes and well-typing predicates. The way to do it is to first define
the graph of the eliminators in the form of inductively-generated relations:
\begin{alignat*}{10}
  & \textsf{data}\ \textsf{R-Con} && :
    (\GG : \textsf{Con}) \to C\ \GG \to \mType \\
  & \textsf{data}\ \textsf{R-Ty} && : \{\GG : \textsf{Con}\} (A : \textsf{Ty}\ \GG)
  (\gamma : C\ \GG)
  \to T\ \GG\ A\ \gamma
  \to \mType
\end{alignat*}
